BERT Model Compression and Weight Sharing

### 2019-05-13 paper/paper.tex
Adding code repository link

Our most important contribution is a new weight-sharing method called
\emph{difference pruning}, which imposes constraint on the sparsity of weight
difference with the pretrained BERT model. While uncompressed fine-tuned BERT
model achieves 92.9\% validation accuracy on SST-2, the difference pruning model
that keeps 99\% of the pretrained BERT weights achieves 91.3\% on the validation
set, which is on par with the fully fine-tuned model. This enables multiple
language modeling tasks to share the weights of pretrained BERT, each incurring
minimal extra storage space requirements.

@@

The challenge that we are facing is therefore how to compress DNNs in size
while keeping their predictive performance competitive with full model. We are interested in compressing the language representation model BERT.  It is the state-of-art result in many natural
language processing tasks  such as natural language inference, paraphrasing
and named entity recognition.

>>>>

Our most important contribution is a new weight-sharing method called
\emph{difference pruning}, which imposes constraint on the sparsity of weight
difference with the pretrained BERT model. While uncompressed fine-tuned BERT
model achieves 92.9\% validation accuracy on SST-2, the difference pruning model
that keeps 99\% of the pretrained BERT weights achieves 91.3\% on the validation
set, which is on par with the fully fine-tuned model. This enables multiple
language modeling tasks to share the weights of pretrained BERT, each incurring
minimal extra storage space requirements.\footnote{Code available at \url{https://github.com/frtennis1/cs287-project}}

@@

We are interested in compressing the language representation model BERT.  It is the state-of-art result in many natural
language processing tasks  such as natural language inference, paraphrasing
and named entity recognition.
